---
title: "Introduction to ```plotBayes```"
output: 
  md_document:
    variant: markdown_github
---

The ```plotBayes``` package illustrates Bayesian inference, showing how the prior distribution and the likelihood of the data combine to produce a posterior distribution.

This is mostly a toy package useful for teaching.

# Installation

You need the ```devtools``` package to install this from github.

```{r, eval=F}
install.packages("devtools")
```

Then install ```plotBayes```.

```{r, eval=F}
devtools::install_github("mcbeem/plotBayes")
```

And then load it.

```{r, echo=T, eval=F}
library(plotBayes)
```

```{r, include=F}
library(plotBayes)
```


# Example

Normal prior with $\mu=0$, $\sigma=0.5$:

```{r, fig.width=5, fig.height=5}
set.seed(1)
data <- rnorm(n=10, mean=1, sd=1)
plotBayes(data, prior.type="normal", prior.parameters=c(0, .5), min=-2, max=2)
```

You can request a different credible interval with with argument ```credible=```.

```{r}
plotBayes(data, prior.parameters=c(.0, .5), prior.type="normal",
          min=-2, max=2, credible=.68)

```

Uniform prior with $a=.7$, $b=1.5$:

```{r}
plotBayes(data, prior.type="uniform", prior.parameters=c(.7, 1.5), min=-2, max=2)
```


